### 2023-10-20 submission/manuscript.Rmd
Replace dot dot with here in relative paths

obs_coverage_files <- glue("../data/{datasets}/data.otu.obs_coverage")
names(obs_coverage_files) <- datasets

@@

rare_coverage_files <- glue("../data/{datasets}/data.otu.rarefy_coverage")
names(rare_coverage_files) <- datasets

>>>>

obs_coverage_files <- here(glue("data/{datasets}/data.otu.obs_coverage"))
names(obs_coverage_files) <- datasets

@@

rare_coverage_files <- here(glue("data/{datasets}/data.otu.rarefy_coverage"))
names(rare_coverage_files) <- datasets
